%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

\cventry
	{Senior Software Engineer} % Job title
	{\href{https://pleo.io/}{Pleo}} % Organization
	{Italy - Full remote} % Location
	{June 2023 - Today} % Date(s)
	{
		Backend engineer in Payments, owning critical flows across authorization, clearing, settlement, refunds and SCA/3DS.\newline
		Promoted to Senior Software Engineer in less than one year.\newline
		Highlights:
		\begin{itemize}
			\item {Led incident response and reliability improvements for core card processing; acted as incident commander and drove follow-ups/runbooks to reduce operational risk.}
			\item {Built observability foundations (dashboards, alerts, synthetic tests) enabling earlier detection and faster debugging of production issues, including business health tracking for transaction processing.}
			\item {Drove 10x-scale readiness work by decomposing/decoupling batch processing into independently deployable components and reducing hot-path bottlenecks.}
			\item {Represented Pleo’s technical perspective in high-stakes discussions with new partners (e.g. migration from a legacy issuer processor to a new one), coordinating technical escalation and cross-team resolution.}
		\end{itemize}
		Most impactful projects:
		\begin{itemize}
			\item {US launch (issuer migration) - delivered transaction processing + integrations to onboard a new issuing platform.}
		  	\item {Multi-currency - clearing + FX conversion reconciliation, improving correctness and unblocking consumers.}
			\item {Spend Controls API - REST endpoints, persistence, domain events; drove architecture/contract alignment.}
		\end{itemize}
	}

%---------------------------------------------------------
	
\cventry
	{Software Engineer} % Job title
	{\href{https://alpian.com/}{Alpian}} % Organization
	{Italy - Full remote} % Location
	{May 2022 - June 2023} % Date(s)
	{
		\begin{itemize}
			\item {Developed the backend for the first Swiss digital private bank, embracing the cloud-native approach with GCP as provider.}
			\item {Built multiple microservices from the ground up in different languages, collaborating with product owners and architects to implement new features while maintaining low tech debt, using agile methodologies (Scrum).}
			\item {Effectively managed legacy services written by an external company, significantly reducing and keeping tech debt under control.}
		\end{itemize}
	}

%---------------------------------------------------------

\cventry
	{Software Engineer} % Job title
	{\href{https://overit.it/en}{OverIT}} % Organization
	{Italy - Full remote} % Location
	{October 2021 - May 2022} % Date(s)
	{
		\begin{itemize}
			\item {Developed and implemented new libraries, increasing code coverage and delivering robustness to application modules.}
			\item {Collaborated with Team Leader to ensure consistent high-quality across entire backend system.}
			\item {Recovered legacy code from untested status, contributing to reliability of core business processes.}
		\end{itemize}
	}

%---------------------------------------------------------

\cventry
    {Software Engineer} % Job title
    {\href{https://i-tel.it}{I-Tel}} % Organization
    {Italy - On site} % Location
    {August 2018 - October 2021} % Date(s)
    {
      	\begin{itemize}
      		\item {Designed and implemented tailored solutions to integrate with external backend systems.}
      		\item {Assisted project manager and sales in pre-sales phase to demonstrate value, trained clients in post-sales phase.}
      		\item {Successfully migrated legacy product platform to new, modular and distributed architecture, leveraging popular frameworks.}
      	\end{itemize}
    }

%---------------------------------------------------------

\end{cventries}
